---
title: "Dual Task"
author: "Eileen Petros"
date: "7/12/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(cowplot)
```

# Constants
```{r}
# Enums
WALK <- 1
VSTROOP <- 2
ASTROOP <- 3

# All in seconds
# TASK_DURATION <- 2
# VSTROOP_INTERVAL <- 1
# ASTROOP_INTERVAL <- 1
# WALK_TRIALS <- 1
# VSTROOP_TRAILS <- 1
# ASTROOP_TRIALS <- 1

TASK_DURATION <- 9
VSTROOP_INTERVAL <- 1.5
ASTROOP_INTERVAL <- 1.5
WALK_TRIALS <- 1
VSTROOP_TRAILS <- 1
ASTROOP_TRIALS <- 1

VSTROOP_STIMULI_COUNT <- TASK_DURATION / VSTROOP_INTERVAL
ASTROOP_STIMULI_COUNT <- TASK_DURATION / ASTROOP_INTERVAL

EVENT_COUNT <- WALK_TRIALS + VSTROOP_STIMULI_COUNT + ASTROOP_STIMULI_COUNT
# StartTrials, WalkTrial, VStroopTrial, AStroopTrial
# TODO change counts to 1, 6, 12, 12
# Depends on interstimulus duration 
EVENT_A <- "# EVENT A - COUNT 1" #start treadmill
EVENT_B <- "# EVENT B - COUNT 1" #walk
EVENT_C <- "# EVENT C - COUNT 2" #vstroop
EVENT_D <- "# EVENT D - COUNT 2" #astroop

filePath <- "./Data/SL_dual0006.csv"
```


# Data Import and Cleaning
```{r}
data <- read.csv(filePath)

data <- as_tibble(data)

# Remove separation lines
data <- data %>% filter(Time != "#")

# Extract summary rows and remove from data
summary <- data %>% slice_tail(n = EVENT_COUNT)
data <- data %>% slice(1:(n() - EVENT_COUNT))


```

# Calculate Force Magnitude
```{r}
data <- data %>% mutate(FP1.Magnitude = 
                              sqrt(FP1.ForX^2 + FP1.ForY^2 + FP1.ForZ^2))
data <- data %>% mutate(FP2.Magnitude = 
                              sqrt(FP2.ForX^2 + FP2.ForY^2 + FP2.ForZ^2))

ggplot(data = data, mapping = 
                            aes(x = Time, y = FP1.Magnitude)) +
  geom_line(size = 0.1, color = "blue") + 
  geom_point(size = 0.1, color = "blue") +
  labs(title = "Force Plate 1 Magnitude", x = "Time", y = "Force") + 
  theme(legend.position =  "none")



```

# Detect Stomp

```{r}
# https://newbedev.com/r-tidyverse-how-to-change-column-data-type-using-pipes-with-least-typing
data$FP1.ForY <- data$FP1.ForY %>% as.double()
data$FP2.ForY <- data$FP2.ForY %>% as.double()

stompTime <- data %>% filter(FP1.ForY == max(FP1.ForY, na.rm = TRUE))
(stompTime$Time <- stompTime$Time %>% as.double())
(stompTime$FP1.ForY)

stompTime2 <- data %>% filter(FP2.ForY == max(FP2.ForY, na.rm = TRUE))
(stompTime2$Time <- stompTime2$Time %>% as.double())
(stompTime$FP2.ForY)
```

# Subset by Stimulus using D-Flow Event Breaks
```{r}
# Find event detection rows
eventBreaks <- data %>%  with(which(is.na(FP1.CopX)))
eventBreaks <- eventBreaks %>% sort()

# break into sets for each event 
sets <- list()
# Ignore first grouping from recording data to 
for (i in 2:(EVENT_COUNT)) {
  # Offset to exclude labels themselves
  start <- (eventBreaks[i] + 1) 
  end <- (eventBreaks[i + 1] - 1)
  varName <- paste0("set", i - 1)
  
  # Don't create indiidual set vars
  #assign(varName, data[start:end,])
  sets[[i - 1]] <- data[start:end,]
}

# Last set
start <- eventBreaks[length(eventBreaks)] + 1
#assign(paste0("set", EVENT_COUNT), data[start :nrow(data),])
sets[[EVENT_COUNT]] <- data[start:nrow(data),]

```

## Final Data Cleaning with All Text Removed
```{r}
data$Time <- as.double(data$Time)
```

# Calculate Average Belt Speed for each Stimulus and Pull Sitmulus Info
```{r}
walkSpeeds <- c()
vStroopSpeeds <- c()
aStroopSpeeds <- c()

vStroopContent <- c()
vStroopCharacteristic <- c()

aStroopContent <- c()
aStroopCharacteristic <- c()

for (i in 1:EVENT_COUNT){
  currentSet <- as_tibble(sets[[i]])
  task <- first(currentSet$Task)
  
  # With character entries in time removed, convert col to double
  currentSet$Time <- as.double(currentSet$Time)
  sets[[i]] <- currentSet
  
  # Compute average speeds
  avgSpeed <- mean(currentSet$LeftBelt.Speed)
  
  if(task == WALK){
    walkSpeeds <- c(walkSpeeds, avgSpeed)
  }
  else if (task == VSTROOP){
    vStroopSpeeds <- c(vStroopSpeeds, avgSpeed)
    # Use first, these values are the same for the entire set
    vStroopContent <- c(vStroopContent, first(currentSet$Stimulus.Content)) 
    vStroopCharacteristic <- c(vStroopCharacteristic, 
                               first(currentSet$Stimulus.Characteristic))
  }
  else if (task == ASTROOP){
    aStroopSpeeds <- c(aStroopSpeeds, avgSpeed)
    aStroopContent <- c(aStroopContent, first(currentSet$Stimulus.Content))
    aStroopCharacteristic <- c(aStroopCharacteristic, 
                               first(currentSet$Stimulus.Characteristic))
  }
  else {
    print("Invlaid task type")
  }
}

walkSpeeds
vStroopSpeeds
aStroopSpeeds
```
## Single Speed Value for Each Task Type
```{r}
(mean(walkSpeeds))
(mean(vStroopSpeeds))
(mean(aStroopSpeeds))
```
# Cognitive Performance
```{r}
print("VStroop Correct Answer: 1 = Red, 2 = Green, 3= Blue, 4 = Yellow, 5 = Purple, 
      6 = Orange, 7 = Gray, 8 = White, 9 = Black")
(vStroopCharacteristic)

print("AStroop Correct Answer: -0.3 = LOW, 0.3 = HIGH")
(aStroopCharacteristic)

print("Results")
vStroopResults <- c(1,1,1,1,1,1)
aStroopResults <- c(1,0,1,1,1,0)

(vStroopResults)
(vStroopPercent <- sum(vStroopResults) / length(vStroopResults))

(aStroopResults)
(aStroopPercent <- sum(aStroopResults) / length(aStroopResults))

```
# Visualizing Forces

```{r}
# dataToPlot <- sets[[6]]
# ggplot(data = dataToPlot, mapping = aes(x = Time, y = FP1.ForY)) + 
#   geom_line() +
#   geom_point() +
#   xlab("Time") + 
#   ylab("Force (N)") 

forcePlate1Plot <- ggplot(data = data, mapping = 
                            aes(x = Time, y = FP1.ForY)) +
  geom_line(size = 0.1, color = "Red") + 
  geom_point(size = 0.1, color = "Red") +
  labs(title = "Force Plate 1 (Y)", x = "Time", y = "Force") + 
  theme(legend.position = "none")

forcePlate2Plot <- ggplot(data = data, mapping = 
                            aes(x = Time, y = FP2.ForY)) +
  geom_line(size = 0.1, color = "blue") + 
  geom_point(size = 0.1, color = "blue") +
  labs(title = "Force Plate 2 (Y)", x = "Time", y = "Force") + 
  theme(legend.position =  "none")


plot_grid(forcePlate1Plot, forcePlate2Plot, ncol = 1, vjust = 0.5)
ggsave(file="./Figures/pilot_force_data.png", width=8, height=4, dpi=300)

ggplot(data = data, mapping = aes(x = Time, y = FP1.ForY)) +
  geom_line(size = 0.1, color = "Red") + 
  geom_line(mapping = aes(y = FP2.ForY), size = 0.1, color = "blue") + 
  labs(title = "Force Plates (Y)", x = "Time", y = "Force") + 
  theme(legend.position = "none")


ggsave(file="./Figures/pilot_force_data_overlay.png", width=8, height=4, dpi=300)

# https://stackoverflow.com/questions/29587881/increase-plot-size-width-in-ggplot2
# 
# Flip axis labesl
# theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust = 1))
 
# ggplot(mm, aes(x = times, y = value)) + geom_line(aes(color = variable)) + 
#       facet_grid(variable ~ ., scales = "free_y") + theme(legend.position = "none")
```


## Isolate Gait Events

### Heel Strike
First nonzero point
```{r}
ggplot(data = set1, mapping = aes(x = Time, y = FP1.ForY)) +
  geom_line() + 
  geom_point(size = 0.1) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust = 1, size = 1))
```
### Toe Off
First return to zero
```{r}

```
